From the function-sheaf dictionary to quasicharacters of $p$-adic tori

### 2015-07-22 dictionary.tex
A few biblio changes, adding invisibility

\keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, character sheaves,smooth commutative group schemes,
finite fields, local fields, algebraic tori, N\'eron models, Greenberg functor, quasicharacters, quasicharacter sheaves.}

@@

\usepackage{amssymb,amsrefs}

@@

@@

\begin{remark}
A descent argument similar to the one employed in the proof of Lemma~\ref{prop:finite} is used in
\cite{boyarchenko-drinfeld:06a}*{Lemma~1.10}, though in the more restrictive case of connected algebraic groups.
\end{remark}

@@

>>>>

\keywords{character sheaves, p-adic tori, N\'eron models, Greenberg functor, geometrization, quasicharacter sheaves}

@@

\usepackage{amssymb}
\usepackage[initials]{amsrefs}

@@

% The publisher wasn't appearing.
\BibSpec{collection.article}{%
    +{}  {\PrintAuthors}				{author}
    +{,} { \textit}						{title}
    +{.} { }							{part}
    +{:} { \textit}						{subtitle}
    +{,} { \PrintContributions}			{contribution}
    +{,} { \PrintConference}				{conference}
    +{}  {\PrintBook}					{book}
    +{,} { }							{booktitle}
    +{}  { \PrintEditorsB}				{editor}
    +{,} { }							{series}
    +{} { \textbf}						{volume}
    +{,} { }							{publisher}
    +{,} { }							{address}
    +{,} { \PrintDateB}					{date}
    +{,} { }							{pages}
    +{,} { }							{status}
    +{,} { \PrintDOI}					{doi}
    +{,} { available at \eprint}			{eprint}
    +{}  { \parenthesize}				{language}
    +{}  { \PrintTranslation}				{translation}
    +{;} { \PrintReprint}				{reprint}
    +{.} { }							{note}
    +{.} {}							{transition}
    +{}  {\SentenceSpace \PrintReviews}	{review}
}

@@

\begin{remark}
A descent argument similar to the one employed in the proof of Lemma~\ref{prop:finite} is used in
\cite{boyarchenko-drinfeld:10a}*{Lemma~1.10}, though in the more restrictive case of connected algebraic groups.
\end{remark}

@@

\begin{definition}
We call a character sheaf $\cs{L}$ on $G$ \emph{invisible} if it is nontrivial and $\TrFrob{G}(\cs{L}) = 1$.
\end{definition}

The proposition gives a method for determining whether a given $G$ admits invisible character sheaves.
